Insert the article title here

### 2018-05-03 writeup/manuscript.tex

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
\caption{Correlation between the two sessions of the \textit{split-half} paradigm for (a)  accuracy (TP-heterogeneous), (b) reaction times and (c) search strategy. (d) initial search strategy correlates with reaction times in both sessions. Each point represents a participant and the error-bars indicate 95\% confidence intervals.}
\label{fig:splithalf_summary}
\end{figure}

@@

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ls_v_ac_mean_log2rt.pdf}}
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ls_v_fg_conj_rt.pdf}}
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ac_v_fg_feature_rt.pdf}}
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ac_v_fg_conj_rt.pdf}}
\subfigure[][]{\includegraphics[width=5cm]{../Scripts/scratch/ls_v_ac_mean_log2rt.pdf}}
\caption{Correlation a) split-half and feature foraging; b) split-half and conjunction foraging, c) adaptive choice and feature  foraging; d) adaptive choice and conjunction foraging; e) split-half and adaptive choice. In all cases, these correlations are low, with $p>0.05$}
\label{fig:between_para_rt}
\end{figure}

>>>>

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/acc_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/rt_correlation.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_corr.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/lineseg/scratch/strat_compare_meanlog_rt.pdf}}
\caption{Each point represents a participant and the error-bars indicate 95\% confidence intervals. Correlation between the two sessions of the \textit{split-half} paradigm for (a)  accuracy (TP-heterogeneous trials only); (b) reaction times and (c) search strategy (TA trials only). (d) Initial search strategy correlates with reaction times in both sessions. }
\label{fig:splithalf_summary}
\end{figure}

@@

\begin{figure}
\centering
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_mean_log2rt.pdf}}
\subfigure[][]{\includegraphics[width=3.25cm]{../Scripts/scratch/ls_v_ac_opt.pdf}}
\caption{Correlation between the split-half and adaptive choice paradigms for (a) reaction times and (b) optimal behaviour.}
\end{figure}
